### 2019-06-12 doc/chapters/towards_verifying_addition.tex
explanation

This is easy.
We just replace all occurrence of A with BigInt, since A is not overrode in an implementing class.
This is not exact the same code, because an implementing class could not override A anymore but that's fine for our verification.

This was a missing feature of Stainless that was fixed on Mai 28, 2019 with \href{https://github.com/epfl-lara/stainless/pull/470}{pull request \mypound470} on GitHub.
Now it should work without this change.

@@

Due to the restrictions on BigInt, we can not use the \& function on.
Simplified code:
\begin{lstlisting}[language=scala]
  sealed abstract class Number extends BasicArithmetic[Int64] {
    def andMask: BigInt

@@

So, we can replace the \& mask with a bound check whether the result is in range of Long.MinValue and Long.MaxValue.
Again the code gets a bit more static and it's not the exact same code anymore.

>>>>

This is easy.
We just replace all occurrence of A with BigInt, since A is not overrode in an implementing class.
This is not exact the same code, because an implementing class can not override A anymore but that's fine for our verification.

This was a missing feature in Stainless that was fixed on Mai 28, 2019 with \href{https://github.com/epfl-lara/stainless/pull/470}{pull request \mypound470} on GitHub.
Now it should work without this change.

@@

Due to the restrictions on BigInt, we can not use the \& function either.
Simplified code:
\begin{lstlisting}[language=scala]
  sealed abstract class Number extends BasicArithmetic[Int64] {
    def andMask: BigInt

@@

So, we can replace the \& mask with a bound check whether the result is in range of Long.MinValue and Long.MaxValue, because Int64 has the same 64-bit range as Long.
Again the code gets a bit more static and it's not the exact same code anymore.
